---
title: "BARCELONA GROUP"
author: "CICERON"
date: '24th October, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(shiny)
library(dplyr)
library(knitr)
library(timevis)

```


## **RESTAURANTS FOR DINNERS** {.tabset .tabset-fade .tabset-pills}

### SHOKO

```{r child='RestShoko.Rmd'}

```

<hr>
  <br><br>
<img src = "MEDIDAS SHOKO.jpg" width="800">
  <br><br>


**COCKTAIL MENU**

    Toast with tomato and Spanish Iberian ham 
    Cod brandade pie 
    Seafood cocktail sppon 
    Cheese selection 
    Wild mushroom croquettes 
    Potato omelette with caramelized onions 
    Crusty squid mini burger with apple dressing 
    Potato cubes with traditional Spanish spicy sauce 
    Brochette of filet steak with mushroom 
    Fish croquettes with fresh tender garlic 
    Prawn wrapped in thin potatoe & black olive pate 
    "Chistorra" (spicy Spanish sausage) and green peppers 
    Mini chocolate foundant 
    Fruit brochettes 
    Catalan creme bruelee shot 
    Soft drins, wine, cava and beer 
    
   
**Important note** _Cocktail dinner in shoko is based in buffet stations. First 20 minutes waiters will serve drinks and food in trays but after this time, guests will go to food stations for dinner. Food stations will be placed at the terrace_


**SEATED DINNER MENU**

    Welcome appetizer
    
    Sushi Moriawase, Shoko chef's selection (8 units)
   
    Grilled filet steak with Perigueux sauce and violet crisp trinxat 
    
    Grilled Octopus with tomato tartar and confit potatoes in pepper 
    
    Chocolate and apricot Sacher Cake 
    
    Wine: luis Cañas (White and red) 
    Water, coffee or tea 

**Important note** _For seated dinner we will have tables at the terrace and in the indoor part. They will have the restaurant in exclusivity for the group_ 
  <br><br>

   


### CDLC 

```{r child='RestCDLC.Rmd'}

```

<hr>
  <br><br>

**COCKTAIL DINNER MENU**
    Cold appetizers 
    Cassava chips with guacamole, coriander and lime 
    "5J" cured ham with crystallized flat bread and tomato 
    Wheat roll filled with chicken, avocado, cheese, spicy mayonnaise and caramelized onion 
    Foie grass "montadito" with apple and spiced mango sauce 
    
    Warm appetizers
    Brie cheese puff pastry with plums, oion and rosemary 
    Red and white quinoa mini burger with avocado, tomato and miso mayonnaise 
    Grilled chicken skewer with portobello mushrooms, spring onion and thyme oil 
    Beef stew with artichokes, oyster mushrooms, beans, confit potatoes, onion and fresh herbs 
    
    Dessert 
    Tiramisu 
    
    Drinks free bar - maximum 2 hours (dinner service)
    Red and white wine, draft beer, water, cava and soft drinks included 

  <br><br>

**SEATED DINNER MENU**

    Appetizer
    Uramaki filled with tuna tartar, banana wrapped in mango and fried onion
    
    Starter
    Red and white quinoa salad with tomato, cucumber, red onion, tofu, raissins and spiced chicken 
    
    Main 
    Basil honey-glazed salmon, couscous, prunes, sliced almonds and asparagus 
    or 
    Sweet chilli marinated grilled chicken, fried rice, peanuts, coriander and lime 
    
    Dessert
    White chocolate mousse, oreo biscuits and mango-passion fruit cream 
    
    Drinks: 
    White wine Vernier 
    Red wine Inpaciente 
    Mineral water 
    Coffee or tea 
   
  

### PRINCIPAL 

```{r child='RestPrincipal.Rmd'}

```
 
 <br> <br>
**COCKTAIL OPTION**
    
    Savoury Snacks 
    
    Mini Ham Croquettes 
    Foie Choux 
    Fried Artichokes 
    Crispy sesame bread with smoked salmon
    Tomato soup Shot 
    Veal Carpaccio toast wit foie mousse and truffle vinaigrette, sundried tomato,     goat cheese and basil brick 
    Hummus with white tuna, sesame and soybeans 
    Truffled bikinis
    Shirmp and green asparagus brochette 
    Truffle rigatonis and parmensan cheese 
    Sirloin steak, onion and mustard 
    
    Desserts (mini pastries)
    Dark and white chocolate tart sweet pastries 
    Leon and merengue pie straberry and mint sorbet 
    Coffee and tea 
   
    
    **Open bar during the cocktail dinner**
    White Wine Ermita D'Espiells D.O. Penedes
    Red withe Sileo D.O. Montsant
    Cava Juve i Camps 
    Water, beers and soft drinks
  <br>


*****

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for  Ciceron Group
  
  * For a group of minimum 300 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done. Availability upon request.
  
*****





